\documentclass[11pt,letter]{moderncv}

% moderncv themes
%\moderncvtheme[blue,sans]{classic}
%\moderncvtheme[blue,sans]{casual}
\moderncvtheme[blue,sans]{banking}
%\moderncvtheme[blue,sans]{oldstyle}
%\moderncvtheme[blue,sans]{fancy}
% optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{microtype}
\usepackage{paralist}
\usepackage{enumitem}

%\setlist{nosep}
\setlist{topsep=1pt,itemsep=3pt,partopsep=1pt,parsep=1pt}
%\setlength{\hintscolumnwidth}{1.75cm}
%\setitemize{itemsep=0pt,topsep=0pt}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


%%%%
%% the following definition is from the file moderncvstyleclassic.sty
%\renewcommand*{\cventry}[7][.25em]{%
%  \cvitem[#1]{#2}{%
%    {\bfseries#3\newline{}}%
%%   \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
%    \ifthenelse{\equal{#4}{}}{}{ {#4 $\mid$}}% ... into this one (without comma).
%    \ifthenelse{\equal{#5}{}}{}{ #5}%
%    \ifthenelse{\equal{#6}{}}{}{ #6}%
%    .\strut%
%    \ifx&#7&%
%      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}
%%%%


\input{moderncv-header.tex}
%\title{Please.}      % optional, remove the line if not wanted
%\address{486 Greene Ave., Apt.\ 2}{Brooklyn, NY}
%\mobile{+30 698 4385057}     % optional, remove the line if not wanted
%\fax{fax (optional)}         % optional, remove the line if not wanted
%\email{mukusano@gmail.com}    % optional, remove the line if not wanted
%\email{\href{mailto:s.dakourou@gmail.com}{s.dakourou@gmail.com}}                      % optional, remove the line if not wanted
%\social[linkedin]{XXX.LINKED.IN.XXX}%{LinkedIn Profile}}                % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle
%
\vspace{-3.5em}
\section{Experience}
\cventry{\large 2018--Present}{\large Program Manager}{\large American Express}{\large New York, New York}{}{}%
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Program manager for three global teams totaling 60 people within the
    Global Billing Network (GBN).
  \item Lead a \$30MM program prioritizing paperless billings within GBN and our
    partners within the organization. This program consists of $20+$ projects
    encompassing multiple international initiatives, including digital
    offerings, marketing, compliance, and communications.
  \item Implemented a program structure by defining scope, milestones,
    workflows, and stakeholder mapping.
    %Communicate these within GBN and
    %the wider organization to ensuring the agreement of all parties.
  \item Interface between the Vice President and the wider team.
    Ensure key strategic priorities are incorporated, and that project
    escalations are reported and resolved. Kept projects on time and on
    budget.
  \item Create presentations for senior leadership, including the executive
    board, ensuring our projects are prioritized within American Express. Requires
    summarizing performance metrics, coordinating with project
    managers, and establishing timelines and a review process. Improved efficiency and quality.
    %improving
    %efficiency and increasing quality.
\end{itemize}
\medbreak
\cventry{\large 2013--2017}{\large Consultant}{\large Deloitte}{\large London, United Kingdom}{}{}%
The following summarizes key projects I worked on while at Deloitte.

%\cventry{}{PMO Analyst}{Fortune 500 and FTSE 100 Listed International Bank}{}{}{%
\textbf{PMO Analyst for HSBC}
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Managed a major international digital learning \& development program.
    This program was complex, on a global scale, and the scope vastly expanded
    throughout the program.
  \item Interfaced between client, program lead, and project teams to
    define program scope and deliverables.
  \item Established program governance by defining team roles and
    responsibilities. Created program plan tracking key milestones and
    deliverables globally across multiple work streams.
  %\item Found payments to vendors were often late and undocumented. Created
  %  billing and invoicing system ensuring payments to outside vendors were on
  %  time and correct.
  %\item Analyzed time and expense tracking in SAP to improve budget and human
  %  resource forecasting.
  %\item Compliance officer ensuring fulfillment of Deloitte's quality and risk
  %  management objectives. Found and resolved outstanding team compliance issues.
\end{itemize}
%}
%\cventry{}{Program Lead}{Internal Respect and Inclusion Program}{}{}{%
\textbf{Program Lead for Deloitte Respect and Inclusion Program}
%
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Spearheaded multi-department respect and inclusion plan altering the
    recruitment, hiring, onboarding, and performance management processes of
    over 1,500 Deloitte employees, and future hires. Supported via analysis of
    company data showing lack of ethnic diversity across grades.
  \item Worked with senior leadership, employee resource groups,
    and HR in creation of plan. Presented to department head, and collaborated with senior
    partners across departments.
\end{itemize}
%\cventry{}{Team Coordinator}{IFRS 17 Business Development}{}{}{%
%\begin{itemize}[label=\large\color{color1}{$\bullet$}]
%  \item Provided support for IFRS 17 requirements within the
%    insurance industry. Worked with SMEs to create training sessions for senior
%    leadership globally within Deloitte's center of excellence.
%  \item Surveyed IFRS 17 expectations from leading industry clientele, conducted
%    competitive analysis, and supported bid and proposal work.
%% 
%\end{itemize}
%}
%\cventry{}{Project Manager}{Leading Global Entertainment and Talent Agency}{}{}{%
\textbf{Project Manager for Endeavor Talent Agency}
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Reported directly to UK partner, and coordinated with global financial
    and IT teams. Agreed on project scope, budget, and timelines.
    Completed quality review/reporting following field testing.
  \item Managed team testing design, implementation, and operating
    effectiveness of key IT SOX controls in accordance with PCAOB standards and
    US best practice.
    %Areas of testing include: data center and
    %network operations, change management, and logical security.
\end{itemize}
%\cventry{}{Head of Employee Engagement}{Deloitte Multicultural Network}{}{}{%
\textbf{Head of Employee Engagement for Deloitte Multicultural Network}
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Sourced and managed external-party relationships to arrange monthly
    events with over 50 attendees.
    %Received positive feedback from attendees and
    %sponsors.
\item Increased accessibility of senior leadership through quarterly live
  interviews.
    %discussing their career challenges and development. Over 100
    %attendees per session.
  \item Created monthly newsletter showcasing diversity in the workplace across
    departments.%, grades, and backgrounds.
\end{itemize}%
%
\section{Education and Qualifications}
% arguments 3 to 6 can be left empty
\cventry{2013--2017}{ACA Chartered Accountant}{Institute of Chartered Accountants in England and Wales}{}{}{}
\cventry{2010--2013}{B.S.\ Business Mathematics and Statistics}{London School of Economics}{}{}{}

\end{document}
