

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{microtype}
\usepackage{xpatch}
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\xpatchcmd{\makeletterclosing}{[3em]}{[0.5em]}{}{}

\input{moderncv-header.tex}

\begin{document}
% recipient data
\recipient{Bloomberg}{731 Lexington Ave.\\New York, NY}
\date{\today}
\opening{Dear Hiring Manager,}
\closing{Warmest Regards,}
\makelettertitle

My interest in Bloomberg began when, as a college student, I visited the London
office. I was awed by the passion of the employees, the international
workforce, and of course the aquariums on every floor! I am delighted this
position is open, as it combines my interest in your company with the guiding
passion of my career: diversity. 
 
I excelled in all the areas listed in the job description. As an
experienced management consultant, I understand complex scenarios, see where
the problems lie, find solutions to these problems, and turn these solutions
into reality. During my time at Deloitte, I noticed the lack of ethnic
diversity across the firm, so I analyzed our internal data comparing it to
outside demographic data. Following this, I developed a multi-department
inclusion strategy, collaborating with senior leadership and HR, which covered
recruitment, performance management, and external partnerships that affected
over 1,500 employees. I’m proud to say that I was the driving force behind
this. What started as a moment’s thought, with no internal support or funding,
became an actionable, data-driven strategy that could be implemented across the
workforce.

On top of this, I was a committee member for the Multicultural Network, one of
Deloitte’s employee networks. As a natural connector, this role allowed me to
creatively exercise my relationship-building skills alongside my analytical
problem-solving abilities.I had no roadmap, a small team, and little funding,
so I relied on my ingenuity and ability to build relationships to turn vision
into reality. I utilized my network to establish an internal mentoring program,
pairing junior and senior employees across departments. Previous mentoring
programs had failed: mine not only succeeded, but was replicated internally
with our consultation. In addition to this, I formulated external partnerships
with other diversity-focused organizations, interviewed senior leadership in
live webinars about their careers, and happily volunteered to speak publicly
about our diversity efforts within the firm. Our network won multiple internal
and external awards, including a European Diversity Award in 2016. I can say
with confidence that my efforts contributed significantly to this achievement.

I am confident I would make an excellent fit at Bloomberg. I have the technical
skills and understanding of organizational dynamics required to affect change.
This, in conjunction with my interpersonal skills, allows me to create tangible
solutions with a human touch. Finally, I am genuinely passionate about
diversity. The work I did resulted in many late nights and false starts, but I
was always enthusiastic because I felt like I was making a difference. 

I am thrilled at the possibility of championing Bloomberg’s D\&I vision. Ever
since my visit to Bloomberg, I have been an admirer of your organization and
its values. I would love to have the opportunity to discuss the value I can
bring to the team and the organization as a whole.

\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
