\documentclass[11pt,letter]{moderncv}

% moderncv themes
\moderncvtheme[blue,sans]{classic}
%\moderncvtheme[blue,sans]{casual}
%\moderncvtheme[blue,sans]{banking}
%\moderncvtheme[blue,sans]{oldstyle}
%\moderncvtheme[blue,sans]{fancy}
% optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{microtype}
\usepackage{paralist}
\usepackage{enumitem}

\setlength{\hintscolumnwidth}{1.75cm}
\setitemize{itemsep=0pt,topsep=0pt}

% adjust the page margins
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Hyperlinks
%\usepackage[pdfpagelabels=false]{hyperref}								% to use hyperlinks
%\definecolor{linkcolour}{rgb}{0,0.2,0.6}			% hyperlinks setup
%\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%%%%
%% the following definition is from the file moderncvstyleclassic.sty
%\renewcommand*{\cventry}[7][.25em]{%
%  \cvitem[#1]{#2}{%
%    {\bfseries#3\newline{}}%
%%   \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
%    \ifthenelse{\equal{#4}{}}{}{ {#4 $\mid$}}% ... into this one (without comma).
%    \ifthenelse{\equal{#5}{}}{}{ #5}%
%    \ifthenelse{\equal{#6}{}}{}{ #6}%
%    .\strut%
%    \ifx&#7&%
%      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}
%%%%


\input{moderncv-header.tex}
%\title{Please.}      % optional, remove the line if not wanted
%\address{486 Greene Ave., Apt.\ 2}{Brooklyn, NY}
%\mobile{+30 698 4385057}     % optional, remove the line if not wanted
%\fax{fax (optional)}         % optional, remove the line if not wanted
%\email{mukusano@gmail.com}    % optional, remove the line if not wanted
%\email{\href{mailto:s.dakourou@gmail.com}{s.dakourou@gmail.com}}                      % optional, remove the line if not wanted
%\social[linkedin]{XXX.LINKED.IN.XXX}%{LinkedIn Profile}}                % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------


\begin{document}
\makecvtitle

\section{Profile}
\vspace{-1.0em}
\cvline{}{
\begin{compactitem}[\large\color{color1}{$\bullet$}]
\item Management consultant with four years' experience managing projects
  end-to-end in the areas of budgeting, risk and controls, team and client
  relationships, and review and reporting.
  \item Led the Employee Engagement team in the Deloitte Multicultural Network, one of Deloitte's ten employee resource groups focused on inclusion.
  %\item Consistently ranked \emph{distinctive}, top 15\% of Deloitte employees, in performance reviews.
  \item Experience in employee engagement, inclusion and diversity policy,
    staff coaching and mentoring, and learning and development.
  \item Consistently ranked in the top 10\% of Deloitte employees in performance reviews.
  %\item Experience in employee engagement, inclusion and diversity policy,
    %staff coaching and mentoring, and learning and development.
\end{compactitem}
}
\vspace{-2.0em}
%
\section{Experience}
\cventry{2013--2017}{Consultant}{Deloitte}{London, United Kingdom}{}{}%
\cventry{}{Head of Employee Engagement}{Deloitte Multicultural Network}{}{}{%
%
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Spearheaded multi-department respect and inclusion plan altering the
    recruitment, hiring, onboarding, and performance management processes of
    over 1,500 existing employees within Deloitte, as well as future hires. 
  \item Analyzed company data and found ethnic diversity within Deloitte did
    not reflect society. Increased data collection, and improved its
    visualization, to promote diverse ethnic representation both in new hires,
    as well as across grades and departments.
  \item Sourced and managed external-party relationships to arrange monthly
    events with over 50 attendees. Received positive feedback from attendees and
    sponsors.
\item Increased accessibility of senior leadership through quarterly live
  interviews discussing their career challenges and development. Over 100
    attendees per session.
  \item Managed team of five in designing and implementing employee
    initiatives.
  \item Created monthly newsletter showcasing diversity in the workplace across
    departments, grades, and backgrounds. Received positive feedback from
    senior leadership.
\end{itemize}%
}
\cventry{}{Project Manager}{FTSE 100 Large International Bank}{}{}{%
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Established and managed major digital learning and development
    transformation program for over 200 international senior executives in the
    areas of: event planning (multiple large-scale international events with
    over 50 attendees), website setup and management, feedback and
    analysis, and billing and budgeting.
  \item Responsible for time and expense tracking, client billing, and
    reporting in SAP. Analyzed and modeled SAP data for presentations to
    management for budget and human resource forecasting.
\end{itemize}
}
%
\cventry{}{Audit Senior}{IT Risk and Controls}{}{}{%
\begin{itemize}[label=\large\color{color1}{$\bullet$}]
  \item Significant experience auditing a range of IT systems and software,
    including specific processes around employee onboarding, offboarding, and
    internal transfer processes.
  \item Advanced Microsoft Office skills, particularly in Excel, for data
    analysis, modelling, automation, and reporting.
\end{itemize}
}
\section{Education and Qualifications}
% arguments 3 to 6 can be left empty
\cventry{2013--2017}{ACA Chartered Accountant}{Institute of Chartered Accountants in England and Wales}{}{}{}
\cventry{2010--2013}{B.S.\ Business Mathematics and Statistics}{London School of Economics}{}{}{}

\end{document}
